\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=1.35cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{microtype}

\definecolor{text}{HTML}{171717}
\definecolor{muted}{HTML}{606060}
\definecolor{rule}{HTML}{D8D8D8}
\definecolor{accent}{HTML}{B45309}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent
}

\pagenumbering{gobble}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\setlength{\emergencystretch}{2em}
\setlist[itemize]{leftmargin=1.2em, topsep=3pt, itemsep=2.5pt, parsep=0pt}

\titleformat{\section}
  {\large\bfseries\color{text}}
  {}{0pt}{}
  [\vspace{-2pt}{\color{rule}\titlerule}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\newcommand{\contactsep}{\quad{\color{muted}|}\quad}
\newcommand{\link}[2]{\href{#1}{#2}}

\newcommand{\educationentry}[4]{%
  \textbf{#1}\hfill{\color{muted}#2}\\
  {\color{muted}#3}\hfill{\color{muted}#4}
}

\newcommand{\projectentry}[4]{%
  \textbf{#1}\hfill\link{#2}{Repository}\\
  {\color{muted}#3}\\[-1pt]
  {\small\color{muted}#4}
}

\newcommand{\projectgap}{\vspace{5pt}}

\begin{document}
\color{text}

{\LARGE\bfseries Edoardo Galli}\\[2pt]
{\large Computer Science student}\\[6pt]
{\small
Bologna, Italy
\contactsep
\link{mailto:edoski.dev@gmail.com}{edoski.dev@gmail.com}
\contactsep
\link{https://edoski.com}{edoski.com}
\contactsep
\link{https://github.com/edoski}{github.com/edoski}
\contactsep
\link{https://www.linkedin.com/in/edoardo-galli-5074321b9}{LinkedIn}
}

\section{Profile}
Computer Science student at the University of Bologna, completing a B.Sc. in Information Science for Management and starting the M.Sc. in Artificial Intelligence in September 2026. Focused on deep learning, AI systems, and typed, reproducible software for data-intensive workflows.

\section{Education}
\educationentry{M.Sc. Artificial Intelligence}{Starts Sep 2026}{University of Bologna}{}

\vspace{4pt}
\educationentry{B.Sc. Information Science for Management}{2021--2026}{University of Bologna}{GPA 28/30}

\vspace{4pt}
\educationentry{International Baccalaureate Diploma}{2017--2021}{International School of Bologna}{Bilingual Diploma}

\section{Languages}
\renewcommand{\arraystretch}{1.15}
\begin{tabularx}{\textwidth}{@{}p{2.9cm}X@{}}
\textbf{English} & Native, IELTS Academic 8.5 \\
\textbf{Italian} & Native \\
\end{tabularx}

\section{Selected Projects}
\projectentry
  {spice}
  {https://github.com/edoski/spice}
  {Temporal fee-decision deep learning pipeline}
  {Python, PyTorch, Optuna, Polars, Pydantic, web3.py}
\begin{itemize}
  \item Built an end-to-end thesis pipeline that turns EVM block history into temporal supervised learning datasets.
  \item Compared LSTM, Transformer, and hybrid model families through reproducible Optuna-driven experiments.
\end{itemize}
\projectgap

\projectentry
  {journal}
  {https://github.com/edoski/journal}
  {Personal analytics journal pipeline}
  {Python, Pydantic, pytest, Obsidian}
\begin{itemize}
  \item Built an automation system syncing Flow focus data, goals, reminders, and daily metrics into Obsidian.
  \item Used typed contracts and protocol ports to keep external integrations explicit and testable.
\end{itemize}
\projectgap

\projectentry
  {sweng-notes}
  {https://github.com/edoski/sweng-notes}
  {Real-time collaborative note editor}
  {Next.js, React, TypeScript, Tailwind CSS, Liveblocks, Convex}
\begin{itemize}
  \item Delivered a shared writing workspace with live presence and typed React surfaces.
  \item Separated durable Convex document state from Liveblocks collaboration state.
\end{itemize}
\projectgap

\projectentry
  {stackoverflow-survey-2025-analysis}
  {https://github.com/edoski/stackoverflow-survey-2025-analysis}
  {AI trust analysis from the Stack Overflow 2025 Developer Survey}
  {Python, scikit-learn, pandas, statsmodels, seaborn}
\begin{itemize}
  \item Modelled developer trust in AI tools with leakage-safe survey preprocessing.
  \item Trained interpretable logistic regression and SVM baselines with GridSearchCV.
\end{itemize}

\section{Technical Skills}
\renewcommand{\arraystretch}{1.22}
\begin{tabularx}{\textwidth}{@{}p{2.9cm}X@{}}
\textbf{Programming} & Python, TypeScript, Java, SQL, PHP \\
\textbf{AI / ML} & PyTorch, scikit-learn, Optuna, pandas, Polars, statsmodels \\
\textbf{Data / Backend} & Pydantic, web3.py, Convex, MySQL, MongoDB, REST, sockets \\
\textbf{Frontend} & Next.js, React, Tailwind CSS, shadcn/ui \\
\textbf{Tools} & Git, Docker, pytest, Bash, Obsidian, Vercel \\
\end{tabularx}

\end{document}
